---
title: "Get started with datavar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with datavar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Basic use

```{r setup}
library(Datavar)
library(knitr)
```

The library *knitr* is loaded for the presentation of the tables. Package *flextable* can also be used with the foot attribute of the table to create a footnote indicating how the variable are described. For now, I use kable but I plan on using *flextable*.

The basical use of datavar is to describe your dataset with default options:

```{r}
# To set the default language to English (French by default)
formals(descr)$langue <- "eng"

# Basic description
datavar_cars <- create_datavar(mtcars)
table_descr <- descr(mtcars, datavar = datavar_cars)
kable(table_descr, row.names = FALSE)
```

This is the basical use for the description, but we can also cross with a variable like the transmission.

```{r}
table_descr_am <- descr(mtcars, y = am, datavar = datavar_cars)
kable(table_descr_am)
```

