---
title: "Get started with datavar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with datavar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Basic use

```{r setup}
library(Datavar)
library(knitr)
```

The library *knitr* is loaded for the presentation of what is the result of the tables. 
Alternatively, function **FlexTabDescr** displays presentation ready tables with help of **flextable** package.

The basical use of datavar is to describe your dataset with default options:

```{r}
# To set the default language to French (English by default)
# formals(descr)$langue <- "eng"

# Basic description
DatavarVoitures <- CreateDatavar(mtcars)
TableDescr <- NoMessDescription(mtcars, .Datavar = DatavarVoitures)
kable(TableDescr, row.names = FALSE)
```

Else we can display it with **flextable**:

```{r}
TableDescr <- NoMessDescription(mtcars, .Datavar = DatavarVoitures, Grapher = TRUE)
FlexTabDescr(TableDescr)
```


This is the basical use for the description, but we can also cross with a variable like the transmission.

```{r}
TableDescrAm <- NoMessDescription(mtcars, .Datavar = DatavarVoitures, y = am)
FlexTabDescr(TableDescrAm)
```

After that you can customize your datavar directly from R as following or you can also directly make it from csv.
Here is the result with fully customized datavar.

```{r}
TableDescrAm <- SilentDescription(mtcars, .Datavar = DatavarMtcars, y = am)
FlexTabDescr(TableDescrAm)
```

# Explore data with plots

If you want to visualize your data quickly, use **visu_data** application (not show in the vignette): you can copy paste the code for the graph to reproduce it out of the application.
Using informations in the datavar, it will select you the plots you can make.


