---
title: "Get started with datavar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with datavar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Basic use

```{r setup}
library(Datavar)
library(knitr)
```

The library *knitr* is loaded for the presentation of the tables. Package *flextable* can also be used with the foot attribute of the table to create a footnote indicating how the variable are described. For now, I use kable but I plan on using *flextable*.

The basical use of datavar is to describe your dataset with default options:

```{r}
# To set the default language to English (French by default)
formals(descr)$langue <- "eng"

# Basic description
datavar_cars <- create_datavar(mtcars)
table_descr <- descr(mtcars, datavar = datavar_cars)
kable(table_descr, row.names = FALSE)
```

This is the basical use for the description, but we can also cross with a variable like the transmission.

```{r}
table_descr_am <- descr(mtcars, y = am, datavar = datavar_cars)
kable(table_descr_am, row.names = FALSE)
```

After that you can customize your datavar directly from R as following or you can also directly make it from csv.

```{r}
datavar_cars$nomvariable <- c("Miles per gallon", "Number of cylinders", "Displacement", 
                              "Gross horsepower", "Rear axle ratio", "Weight (1000 lbs)", "Quarter mile time (sec)", 
                              "Straight engine", "Manual transmission", "Number of forward gears", 
                              "Number of carburetors")
table_descr_am <- descr(mtcars, y = am, datavar = datavar_cars)
kable(table_descr_am, row.names = FALSE)
```

And now you have your variables' names. If you want to visualize your data quickly, use **visu_data** application (not show in the vignette): you can copy paste the code for the graph to reproduce it out of the application.
